Manuscript

### 2015-01-27 inst/simulation/manuscript.Rmd
...

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed))
    y <- lm(Estimated~Observed, x)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), Failed=failed))
  }, overEstimate=overEstimate)

@@

dir <- normalizePath(context$figuresDirectory)
getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
```

>>>>

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed))
    y <- lm(Estimated~Observed, x)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), Failed=failed))
  }, overEstimate=overEstimate)

@@

dir <- normalizePath(context$figuresDirectory)
table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
logTable1$EstDev <- table1$EstDev
write.csv(logTable1, file=file.path(dir, "table-1a.csv"))

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
logTable2$EstDev <- table2$EstDev
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
logTable3$EstDev <- table3$EstDev
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```
